---
title: "SIOP 2016 Master Tutorial on Reproducible Research_FINAL_pander"
author: "Rob S."
date: "April 16, 2016"
output:
  pdf_document:
    toc: yes
  html_document:
    theme: united
    toc: yes
  word_document:
    toc: yes
csl: apa.csl
bibliography: citations.bib
---

```{r global_options, fig.width=14, fig.height=8, fig.path='Figs/', echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
#knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
#                      echo=TRUE, warning=FALSE, message=FALSE)
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo=FALSE)
```


```{r, message=FALSE}
#tryCatch code to load all necessary packages
tryCatch(require(knitr),finally=utils:::install.packages(pkgs='knitr',repos='http://cran.r-project.org'));
require(knitr)

tryCatch(require(evaluate),finally=utils:::install.packages(pkgs='evaluate',repos='http://cran.r-project.org'));
require(evaluate)

#tryCatch code to load all necessary packages
tryCatch(require(RCurl),finally=utils:::install.packages(pkgs='RCurl',repos='http://cran.r-project.org'));
require(RCurl)

tryCatch(require(psych),finally=utils:::install.packages(pkgs='psych',repos='http://cran.r-project.org'));
require(psych)

tryCatch(require(sjPlot),finally=utils:::install.packages(pkgs='sjPlot',repos='http://cran.r-project.org'));
require(sjPlot)

tryCatch(require(quantreg),finally=utils:::install.packages(pkgs='quantreg',repos='http://cran.r-project.org'));
require(quantreg)

tryCatch(require(dplyr),finally=utils:::install.packages(pkgs='dplyr',repos='http://cran.r-project.org'));
require(dplyr)

tryCatch(require(pastecs),finally=utils:::install.packages(pkgs='pastecs',repos='http://cran.r-project.org'));
require(pastecs)

#tryCatch code to load all necessary packages
tryCatch(require(pander),finally=utils:::install.packages(pkgs='pander',repos='http://cran.r-project.org'));
require(pander)

#tryCatch code to load all necessary packages
tryCatch(require(Hmisc),finally=utils:::install.packages(pkgs='Hmisc',repos='http://cran.r-project.org'));
require(Hmisc)
```



```{r}
library(RCurl)
x <- getURL("https://raw.githubusercontent.com/RobStilson/SIOP_2016_Master_Tutorial/master/mydata_10k.csv")
mydata_10k <- read.csv(text = x)

#Pulling a random sample of 1000
set.seed(1)
mydata <- mydata_10k[ sample( which(mydata_10k$country=='USA'), 1000, replace=FALSE),]
#Remove # in front of `mydata` on the line below and put # in front of `mydata` on the line above to load the 10,000 applicant sample.
#mydata <- mydata_10k
```


#SIOP 2016 Reproducible Research Master Tutorial

##Introduction

The purpose of this study is to briefly go over some of the ways you can use R Markdown for creating documents. The data utilized in this study comes from [Johnson's IPIP-NEO data repository](https://osf.io/wxvth/). This repository contains data from the [International Personality Item Pool](http://ipip.ori.org/) (IPIP) for both the 300 item version and the 120 item version. The data for the 300 item version contains 307,313 respondents from around the world and the data for the 120 item version has 619,150 respondents. Additional information regarding these studies is available on Johnson's web site and in [@johnson2014measuring].

##Study

This study looks at coefficient alpha [@cronbach1951coefficient] to determine the internal reliability of the scales of the IPIP120 which correspond to the constructs of the NEO-PI-R [@costa1992neo]. Reliability will be calculated at the overall scale level and not at the facet level. Table 1 gives a break down of the five scales and the facets that make up each scale.

###Table 1. IPIP120 Scales and Facets.

+------------------------+------------------------+
| Scale                  | Facets                 |
+========================+========================+
| Agreeableness          | - Trust                |
|                        | - Morality             |
|                        | - Altruism             |              
|                        | - Cooperation          |
|                        | - Modesty              |
|                        | - Sympathy             |
+------------------------+------------------------+
| Conscientiousness      | - Self-Efficacy        |
|                        | - Orderliness         |
|                        | - Dutifulness          |
|                        | - Achievement-Striving |
|                        | - Self-Discipline      |
|                        | - Cautiousness         |
+------------------------+------------------------+
| Extraversion           | - Friendliness         |
|                        | - Gregariousness       |
|                        | - Assertiveness        |
|                        | - Activity Level       |
|                        | - Excitement-Seeking   |
|                        | - Cheerfulness         |
+------------------------+------------------------+
| Neuroticism            | - Anxiety              |
|                        | - Anger                |
|                        | - Depression           |
|                        | - Self-Consciousness   |
|                        | - Immoderation         |
|                        | - Vulnerability        |
+------------------------+------------------------+
| Openness               | - Imagination          |
|                        | - Artistic Interest    |
|                        | - Emotionality         |
|                        | - Adventurousness      |
|                        | - Intellect            |
|                        | - Liberalism           |
+------------------------+------------------------+

##Method

For this study we took a random sample of `r formatC(nrow(mydata), big.mark = ',')` from the United States. The average age of the participant was `r round(mean(mydata$age))` and the gender split was `r sum((mydata$sex=='2')/nrow(mydata))*100`% female. 


```{r}
# recode 0 (missing response) to NA across multiple columns
#From: http://onertipaday.blogspot.com/2009/06/replacing-0-with-na-evergreen-from-list.html

#And

#From: https://stackoverflow.com/questions/14737773/replacing-occurrences-of-a-number-in-multiple-columns-of-data-frame-with-another

mydata[,11:130][mydata[,11:130] ==0] <- NA
```


```{r}
#Renaming variables

# rename programmatically 
library(reshape)
#mydata <- rename(mydata, c(oldname="newname"))

mydata <- rename(mydata, c(i1="N1_Anxiety_1"))#Worry about things.
mydata <- rename(mydata, c(i2="E1_Friendliness_2"))#Make friends easily.
mydata <- rename(mydata, c(i3="O1_Imagination_3"))#Have a vivid imagination.
mydata <- rename(mydata, c(i4="A1_Trust_4"))#Trust others.
mydata <- rename(mydata, c(i5="C1_Self-Efficacy_5"))#Complete tasks successfully.
mydata <- rename(mydata, c(i6="N2_Anger_6"))#Get angry easily.
mydata <- rename(mydata, c(i7="E2_Gregariousness_7"))#Love large parties.
mydata <- rename(mydata, c(i8="O2_Artistic Interests_8"))#Believe in the importance of art.
mydata <- rename(mydata, c(i9="A2_Morality_9"))#Use others for my own ends.
mydata <- rename(mydata, c(i10="C2_Orderliness_10"))#Like to tidy up.
mydata <- rename(mydata, c(i11="N3_Depression_11"))#Often feel blue.
mydata <- rename(mydata, c(i12="E3_Assertiveness_12"))#Take charge.
mydata <- rename(mydata, c(i13="O3_Emotionality_13"))#Experience my emotions intensely.
mydata <- rename(mydata, c(i14="A3_Altruism_14"))#Love to help others.
mydata <- rename(mydata, c(i15="C3_Dutifulness_15"))#Keep my promises.
mydata <- rename(mydata, c(i16="N4_Self-Consciousness_16"))#Find it difficult to approach others.
mydata <- rename(mydata, c(i17="E4_Activity Level_17"))#Am always busy.
mydata <- rename(mydata, c(i18="O4_Adventurousness_18"))#Prefer variety to routine.
mydata <- rename(mydata, c(i19="A4_Cooperation_19"))#Love a good fight.
mydata <- rename(mydata, c(i20="C4_Achievement-Striving_20"))#Work hard.
mydata <- rename(mydata, c(i21="N5_Immoderation_21"))#Go on binges.
mydata <- rename(mydata, c(i22="E5_Excitement-Seeking_22"))#Love excitement.
mydata <- rename(mydata, c(i23="O5_Intellect_23"))#Love to read challenging material.
mydata <- rename(mydata, c(i24="A5_Modesty_24"))#Believe that I am better than others.
mydata <- rename(mydata, c(i25="C5_Self-Discipline_25"))#Am always prepared.
mydata <- rename(mydata, c(i26="N6_Vulnerability_26"))#Panic easily.
mydata <- rename(mydata, c(i27="E6_Cheerfulness_27"))#Radiate joy.
mydata <- rename(mydata, c(i28="O6_Liberalism_28"))#Tend to vote for liberal political candidates.
mydata <- rename(mydata, c(i29="A6_Sympathy_29"))#Sympathize with the homeless.
mydata <- rename(mydata, c(i30="C6_Cautiousness_30"))#Jump into things without thinking.
mydata <- rename(mydata, c(i31="N1_Anxiety_31"))#Fear for the worst.
mydata <- rename(mydata, c(i32="E1_Friendliness_32"))#Feel comfortable around people.
mydata <- rename(mydata, c(i33="O1_Imagination_33"))#Enjoy wild flights of fantasy.
mydata <- rename(mydata, c(i34="A1_Trust_34"))#Believe that others have good intentions.
mydata <- rename(mydata, c(i35="C1_Self-Efficacy_35"))#Excel in what I do.
mydata <- rename(mydata, c(i36="N2_Anger_36"))#Get irritated easily.
mydata <- rename(mydata, c(i37="E2_Gregariousness_37"))#Talk to a lot of different people at parties.
mydata <- rename(mydata, c(i38="O2_Artistic Interests_38"))#See beauty in things that others might not notice.
mydata <- rename(mydata, c(i39="A2_Morality_39"))#Cheat to get ahead.
mydata <- rename(mydata, c(i40="C2_Orderliness_40"))#Often forget to put things back in their proper place.
mydata <- rename(mydata, c(i41="N3_Depression_41"))#Dislike myself.
mydata <- rename(mydata, c(i42="E3_Assertiveness_42"))#Try to lead others.
mydata <- rename(mydata, c(i43="O3_Emotionality_43"))#Feel others' emotions.
mydata <- rename(mydata, c(i44="A3_Altruism_44"))#Am concerned about others.
mydata <- rename(mydata, c(i45="C3_Dutifulness_45"))#Tell the truth.
mydata <- rename(mydata, c(i46="N4_Self-Consciousness_46"))#Am afraid to draw attention to myself.
mydata <- rename(mydata, c(i47="E4_Activity Level_47"))#Am always on the go.
mydata <- rename(mydata, c(i48="O4_Adventurousness_48"))#Prefer to stick with things that I know.
mydata <- rename(mydata, c(i49="A4_Cooperation_49"))#Yell at people.
mydata <- rename(mydata, c(i50="C4_Achievement-Striving_50"))#Do more than what's expected of me.
mydata <- rename(mydata, c(i51="N5_Immoderation_51"))#Rarely overindulge.
mydata <- rename(mydata, c(i52="E5_Excitement-Seeking_52"))#Seek adventure.
mydata <- rename(mydata, c(i53="O5_Intellect_53"))#Avoid philosophical discussions.
mydata <- rename(mydata, c(i54="A5_Modesty_54"))#Think highly of myself.
mydata <- rename(mydata, c(i55="C5_Self-Discipline_55"))#Carry out my plans.
mydata <- rename(mydata, c(i56="N6_Vulnerability_56"))#Become overwhelmed by events.
mydata <- rename(mydata, c(i57="E6_Cheerfulness_57"))#Have a lot of fun.
mydata <- rename(mydata, c(i58="O6_Liberalism_58"))#Believe that there is no absolute right or wrong.
mydata <- rename(mydata, c(i59="A6_Sympathy_59"))#Feel sympathy for those who are worse off than myself.
mydata <- rename(mydata, c(i60="C6_Cautiousness_60"))#Make rash decisions.
mydata <- rename(mydata, c(i61="N1_Anxiety_61"))#Am afraid of many things.
mydata <- rename(mydata, c(i62="E1_Friendliness_62"))#Avoid contacts with others.
mydata <- rename(mydata, c(i63="O1_Imagination_63"))#Love to daydream.
mydata <- rename(mydata, c(i64="A1_Trust_64"))#Trust what people say.
mydata <- rename(mydata, c(i65="C1_Self-Efficacy_65"))#Handle tasks smoothly.
mydata <- rename(mydata, c(i66="N2_Anger_66"))#Lose my temper.
mydata <- rename(mydata, c(i67="E2_Gregariousness_67"))#Prefer to be alone.
mydata <- rename(mydata, c(i68="O2_Artistic Interests_68"))#Do not like poetry.
mydata <- rename(mydata, c(i69="A2_Morality_69"))#Take advantage of others.
mydata <- rename(mydata, c(i70="C2_Orderliness_70"))#Leave a mess in my room.
mydata <- rename(mydata, c(i71="N3_Depression_71"))#Am often down in the dumps.
mydata <- rename(mydata, c(i72="E3_Assertiveness_72"))#Take control of things.
mydata <- rename(mydata, c(i73="O3_Emotionality_73"))#Rarely notice my emotional reactions.
mydata <- rename(mydata, c(i74="A3_Altruism_74"))#Am indifferent to the feelings of others.
mydata <- rename(mydata, c(i75="C3_Dutifulness_75"))#Break rules.
mydata <- rename(mydata, c(i76="N4_Self-Consciousness_76"))#Only feel comfortable with friends.
mydata <- rename(mydata, c(i77="E4_Activity Level_77"))#Do a lot in my spare time.
mydata <- rename(mydata, c(i78="O4_Adventurousness_78"))#Dislike changes.
mydata <- rename(mydata, c(i79="A4_Cooperation_79"))#Insult people.
mydata <- rename(mydata, c(i80="C4_Achievement-Striving_80"))#Do just enough work to get by.
mydata <- rename(mydata, c(i81="N5_Immoderation_81"))#Easily resist temptations.
mydata <- rename(mydata, c(i82="E5_Excitement-Seeking_82"))#Enjoy being reckless.
mydata <- rename(mydata, c(i83="O5_Intellect_83"))#Have difficulty understanding abstract ideas.
mydata <- rename(mydata, c(i84="A5_Modesty_84"))#Have a high opinion of myself.
mydata <- rename(mydata, c(i85="C5_Self-Discipline_85"))#Waste my time.
mydata <- rename(mydata, c(i86="N6_Vulnerability_86"))#Feel that I'm unable to deal with things.
mydata <- rename(mydata, c(i87="E6_Cheerfulness_87"))#Love life.
mydata <- rename(mydata, c(i88="O6_Liberalism_88"))#Tend to vote for conservative political candidates.
mydata <- rename(mydata, c(i89="A6_Sympathy_89"))#Am not interested in other people's problems.
mydata <- rename(mydata, c(i90="C6_Cautiousness_90"))#Rush into things.
mydata <- rename(mydata, c(i91="N1_Anxiety_91"))#Get stressed out easily.
mydata <- rename(mydata, c(i92="E1_Friendliness_92"))#Keep others at a distance.
mydata <- rename(mydata, c(i93="O1_Imagination_93"))#Like to get lost in thought.
mydata <- rename(mydata, c(i94="A1_Trust_94"))#Distrust people.
mydata <- rename(mydata, c(i95="C1_Self-Efficacy_95"))#Know how to get things done.
mydata <- rename(mydata, c(i96="N2_Anger_96"))#Am not easily annoyed.
mydata <- rename(mydata, c(i97="E2_Gregariousness_97"))#Avoid crowds.
mydata <- rename(mydata, c(i98="O2_Artistic Interests_98"))#Do not enjoy going to art museums.
mydata <- rename(mydata, c(i99="A2_Morality_99"))#Obstruct others' plans.
mydata <- rename(mydata, c(i100="C2_Orderliness_100"))#Leave my belongings around.
mydata <- rename(mydata, c(i101="N3_Depression_101"))#Feel comfortable with myself.
mydata <- rename(mydata, c(i102="E3_Assertiveness_102"))#Wait for others to lead the way.
mydata <- rename(mydata, c(i103="O3_Emotionality_103"))#Don't understand people who get emotional.
mydata <- rename(mydata, c(i104="A3_Altruism_104"))#Take no time for others.
mydata <- rename(mydata, c(i105="C3_Dutifulness_105"))#Break my promises.
mydata <- rename(mydata, c(i106="N4_Self-Consciousness_106"))#Am not bothered by difficult social situations.
mydata <- rename(mydata, c(i107="E4_Activity Level_107"))#Like to take it easy.
mydata <- rename(mydata, c(i108="O4_Adventurousness_108"))#Am attached to conventional ways.
mydata <- rename(mydata, c(i109="A4_Cooperation_109"))#Get back at others.
mydata <- rename(mydata, c(i110="C4_Achievement-Striving_110"))#Put little time and effort into my work.
mydata <- rename(mydata, c(i111="N5_Immoderation_111"))#Am able to control my cravings.
mydata <- rename(mydata, c(i112="E5_Excitement-Seeking_112"))#Act wild and crazy.
mydata <- rename(mydata, c(i113="O5_Intellect_113"))#Am not interested in theoretical discussions.
mydata <- rename(mydata, c(i114="A5_Modesty_114"))#Boast about my virtues.
mydata <- rename(mydata, c(i115="C5_Self-Discipline_115"))#Have difficulty starting tasks.
mydata <- rename(mydata, c(i116="N6_Vulnerability_116"))#Remain calm under pressure.
mydata <- rename(mydata, c(i117="E6_Cheerfulness_117"))#Look at the bright side of life.
mydata <- rename(mydata, c(i118="O6_Liberalism_118"))#Believe that we should be tough on crime.
mydata <- rename(mydata, c(i119="A6_Sympathy_119"))#Try not to think about the needy.
mydata <- rename(mydata, c(i120="C6_Cautiousness_120"))#Act without thinking.

```

Table 2 contains the descriptive statistics by item.

###Table 2 Descriptive statistics by item
```{r}
library(pastecs)
options(scipen=100)#setting scientific notation
options(digits=2)#setting number of digits displayed
summary_stats_mydata <- stat.desc(mydata, basic=F)#summary statistics
summary_stats_mydata_trans <- as.data.frame(t(summary_stats_mydata))#transposing and saving as a data frame
summary_stats_mydata_trans <- summary_stats_mydata_trans[-c(1:10),]#removing the first 10 rows so we only have items left
summary_stats_mydata_trans <- round(summary_stats_mydata_trans,2)
summary_stats_mydata_trans <- summary_stats_mydata_trans[-c(3:5,7)]#removing unnecessary columns

#summary_stats_mydata_trans <- cbind(Items = rownames(summary_stats_mydata_trans), summary_stats_mydata_trans)
# add the rownames as a proper column
#myDF <- cbind(Row.Names = rownames(myDF), myDF)
#From: https://stackoverflow.com/questions/17514648/how-do-i-name-the-row-names-column-in-r

library(pander)
pander(summary_stats_mydata_trans)

#library(sjPlot)
#summary_stats_mydata_table <- sjt.df(summary_stats_mydata_trans, title = "Descriptive Stats", alternateRowColors=TRUE, useViewer=F, describe=FALSE,encoding = "UTF-8", no.output=TRUE, hideProgressBar = TRUE)$knitr
```


```{r}
items <- mydata[c(11:130)]

keys <- make.keys(nvars=120, list(
    AGR=c(4,-9,14,-19,-24,29,34,-39,44,-49,-54,59,64,-69,-74,-79,-84,-89,-94,-99,-104,-109,-114,-119),
    CON=c(5,10,15,20,25,-30,35,-40,45,50,55,-60,65,-70,-75,-80,-85,-90,95,-100,-105,-110,-115,-120), 
    EXT=c(2,7,12,17,22,27,32,37,42,47,52,57,-62,-67,72,77,82,87,-92,-97,-102,	-107,112,117),
    NEU=c(1,6,11,16,21,26,31,36,41,46,-51,56,61,66,71,76,-81,86,91,-96,-101,-106,-111,-116),
    OPN=c(3,8,13,18,23,28,33,38,43,-48,-53,58,63,-68,-73,-78,-83,-88,93,-98,	-103,-108,-113,-118)),
    item.labels=(colnames(items)))
```


```{r}
scores <- scoreItems(keys, items)
```
Alpha reliabilities are located in Table 3.

###Table 3: Alpha reliabilities
```{r}
scores_alpha <- round(as.data.frame(scores$alpha), 3)
pander(scores_alpha)

#scores_alpha_table <- sjt.df(scores_alpha, title = "Alpha Reliability of Scales", alternateRowColors=TRUE, useViewer=F, describe=FALSE,encoding = "UTF-8", no.output=TRUE, hideProgressBar = TRUE)$knitr
```





```{r}
#Creating total scores
library(dplyr)

mydata_test <- items %>%
    mutate(AGR_Total = rowSums(items[c(4,9,14,19,24,29,34,39,44,49,54,59,64,69,74,79,84,89,94,99,104,109,114,119)])) %>%
    mutate(CON_Total = rowSums(items[c(5,10,15,20,25,30,35,40,45,50,55,60,65,70,75,80,85,90,95,100,105,110,115,120)])) %>%
    mutate(EXT_Total = rowSums(items[c(2,7,12,17,22,27,32,37,42,47,52,57,62,67,72,77,82,87,92,97,102,	107,112,117)])) %>%
    mutate(NEU_Total = rowSums(items[c(1,6,11,16,21,26,31,36,41,46,51,56,61,66,71,76,81,86,91,96,101,106,111,116)])) %>%
    mutate(OPN_Total = rowSums(items[c(3,8,13,18,23,28,33,38,43,48,53,58,63,68,73,78,83,88,93,98,103,108,113,118)]))


#round(describe(mydata_test), 3)
#round(describe(mydata_test[c(121:125)]), 3)
```


###Table 4: Correlations between scale total scores
```{r}
#corstarsl
#From: http://myowelt.blogspot.com/2008/04/beautiful-correlation-tables-in-r.html
corstarsl <- function(x){ 
library(Hmisc) 
x <- as.matrix(x) 
R <- rcorr(x)$r 
p <- rcorr(x)$P 

## define notions for significance levels; spacing is important.
mystars <- ifelse(p < .001, "***", ifelse(p < .01, "** ", ifelse(p < .05, "* ", " ")))

## trunctuate the matrix that holds the correlations to two decimal
R <- format(round(cbind(rep(-1.11, ncol(x)), R), 2))[,-1] 

## build a new matrix that includes the correlations with their apropriate stars 
Rnew <- matrix(paste(R, mystars, sep=""), ncol=ncol(x)) 
diag(Rnew) <- paste(diag(R), " ", sep="") 
rownames(Rnew) <- colnames(x) 
colnames(Rnew) <- paste(colnames(x), "", sep="") 

## remove upper triangle
Rnew <- as.matrix(Rnew)
Rnew[upper.tri(Rnew, diag = TRUE)] <- ""
Rnew <- as.data.frame(Rnew) 

## remove last column and return the matrix (which is now a data frame)
Rnew <- cbind(Rnew[1:length(Rnew)-1])
return(Rnew) 
}

pander(corstarsl(mydata_test[,121:125]))
    
#corr_table <- sjt.corr(mydata_test[c(121:125)], corMethod = "pearson", digits=3, triangle = "lower", title = "Correlation of Scales", encoding = "UTF-8", no.output=TRUE)$knitr
```

##Data Visualization

Figure 1 contains a scatter plot of matrices (SPLOM) of the average score (as opposed to total score in Table 4) on each scale. This plot contains a bivariate scatter plot below the diagonal, histograms on the diagonal, and the Pearson correlation above the diagonal.

###Figure 1: Scatter plot of average scale scores matrices
```{r}
pairs.panels(scores$scores,pch='.',jiggle=TRUE)
``` 

##Results

The alpha reliability analysis for this sample indicates that none of the five scales reached the commonly accepted threshold of $\alpha$ = .70 (@nunnally1970introduction).

##Discussion

Our reliabilities differed significantly from [@johnson2014measuring]'s results. See Table 5 for the comparison. These differences may be due to sampling error. Limitations of this study include using a relatively small sample size compared the sample size available, (`r formatC(nrow(mydata), big.mark = ',')` vs 619,150), and only sampling from the United States. Future studies could use larger sample sizes and include more countries than just the United States.

###Table 5

Scale             | Current Study    |  Johnson (2014)
----------------- | :-------------:  | :--------------:
Neuroticism       | 0.69             | 0.90
Extraversion      | 0.64             | 0.89
Openness          | 0.12             | 0.83
Agreeableness     | 0.59             | 0.87
Conscientiousness | 0.46             | 0.90

###Table 6

Scale             | Current Study   |  Johnson (2014)
----------------- | :-------------: | :--------------:
Neuroticism       | `r round(scores_alpha$NEU,2)` | 0.90
Extraversion      | `r round(scores_alpha$EXT,2)` | 0.89
Openness          | `r round(scores_alpha$OPN,2)` | 0.83
Agreeableness     | `r round(scores_alpha$AGR,2)` | 0.87
Conscientiousness | `r round(scores_alpha$CON,2)` | 0.90

##References
